Estimating the magnetization distribution within rectangular rock samples

### 2016-06-24 manuscript/manuscript.tex

\usepackage{rotating}
\usepackage{amsmath}

@@

Over the last decades, scanning magnetic microscopy techniques have 
been increasingly used in paleomagnetism and rock magnetism. 
Different from standard paleomagnetic magnetometers, scanning 
magnetic microscopes produce high-resolution maps of the vertical 
component of the magnetic induction field (flux density) 
on a plane located over the sample. 
These high-resolution magnetic maps can be used for estimating the 
magnetization distribution within a rock sample by inversion.
Previous studies have estimated the magnetization distribution 
within rock samples by inverting the magnetic data measured on a 
single plane above the sample. Here we present a new spatial domain
method for inverting the magnetic induction measured on four 
planes around the sample in order to retrieve its internal 
magnetization distribution. We have presumed that the internal 
magnetization distribution of the sample varies along one of
its axes. Our method approximates the sample geometry
by an interpretation model composed of a one-dimensional 
array of juxtaposed rectangular prisms with uniform magnetization. 
The Cartesian components of the magnetization vector 
within each rectangular prism 
are the parameters to be estimated by solving a linear inverse problem. 
Our method automatically deals with the averaging of 
the measured magnetic data due to the finite size of the magnetic sensor,
preventing the application of a deconvolution before the inversion.
Tests with synthetic data show the performance of our method in 
retrieving complex magnetization distributions even in 
the presence of magnetization heterogeneities. 
We have also applied our method to invert experimentally measured 
magnetic data produced by a highly-magnetized synthetic sample 
that was manufactured in the laboratory.
The results show that, even in the presence of apparent position
noise, our method was able to retrieve the magnetization distribution
consistent with the isothermal remanent magnetization
induced in the sample.

@@

We have inverted magnetic data produced by
numerical simulations with the purpose of illustrating not only the 
good performance of our method in ideal cases, but also how
the estimated magnetization distribution obtained by our
method can be negatively impacted by the presence of position 
noise, errors in the sensor-to-sample distance and 
pre-processing errors in the observed data.
Tests with synthetic data simulating a real ferro-manganese
crust with magnetization heterogeneities show that our method 
can be used, for example, in fine-scale magnetostratigraphic 
studies.
We have also shown the results obtained by applying our method
to invert experimentally measured magnetic data produced by
a highly-magnetized synthetic sample that was manufactured in 
laboratory.
The results show that our method is able to estimate a magnetization
distribution that is consistent with the Isothermal Remanence 
Magnetization (IRM) induced in the
sample, even by inverting a magnetic data set that is contaminated 
by apparent position noise and were measured by a
custom-made magnetometer based on a Hall sensor.

@@

@@

Figure \ref{fig:estimate-validation} shows the four estimated 
magnetization distributions obtained by our method.
The one obtained by inverting the magnetic data on the 
four planes $\alpha = 0, 1, 2, 3$ is represented by the 
black dots and dashed lines. 
The three sets of blue dots and 
dashed lines represent the estimated magnetization distribution 
obtained by inverting the data located on the plane 
$\alpha = 0$, planes $\alpha = 0, 1$ and planes $\alpha = 0, 1, 2$,
which are plotted, respectively, with high, intermediate and low 
transparency.
We can see that the estimated magnetization distribution 
obtained by inverting the full data set (black dots and black 
dashed lines in Figure \ref{fig:estimate-validation}) is the best one
in retrieving the true magnetization distribution
(red dots and red lines in Figure \ref{fig:estimate-validation}).
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-validation}b, e, h and k) that is very
close to the observed data (Figures \ref{fig:datafit-validation}a, 
d, g and j).
The normalized histograms of the residuals between the predicted and
observed data (Figures \ref{fig:datafit-validation}c, f, i and l) show
sample means $\mu$ and sample standard deviations $\sigma$
very close to that ones of the pseudo-random noise 
contaminating the simulated magnetic data.

@@

Figure \ref{fig:estimate-pre-processing} confirms the
the superiority of the estimated magnetization distribution 
obtained by inverting the full data set (black dots and 
black dashed lines) over the other three (blue dots and blue dashed lines).
We can see, however, that even the estimated obtained with
the full data set failed in
retrieving the magnetization distribution of the simulated sample
(red dots). 
This poorly-estimated magnetization distribution yields 
predicted data (Figures \ref{fig:datafit-pre-processing}b, e, h and k) 
that do not
recover the observed data (Figures \ref{fig:datafit-pre-processing}a, 
d, g and j).
This coarse data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-pre-processing}c, f, i and l).
The sample means $\mu$ would be very close to the simulated 
constant bias and the sample standard deviations $\sigma$ would
be very close to that one of the pseudo-random noise 
if the magnetic data were properly corrected from
the misalignment problems.

These results exemplify the effects of not correcting the
misalignment problems prior to the inversion.
As we can see, these problems lead to an estimated magnetization 
distribution that do not retrieves the true one and also
produce a coarse data fit.

@@

Unlike the previous tests, the distance $h$ 
(Figure \ref{fig:sample-planes-cross}) between the 
surface of the sample and the observation
points at each plane is not constant.
Let us first remember that, on each plane $\alpha = 0, 1, 2, 3$,
the observation points are located on a set 
of $42$ regularly-spaced acquisition 
lines, each one with $102$ regularly spaced points.
In this test, the distance $h$ is contaminated with a
Gaussian position noise having a common standard deviation of
$100$~$\mu$m and a different mean value equal to 
$420$~$\mu$m, $330$~$\mu$m, $400$~$\mu$m and $230$~$\mu$m
on each plane $\alpha = 0, 1, 2, 3$, respectively.
The distance $h$, however, is constant for observation points 
located on the same acquisition line.

@@

Figure \ref{fig:estimate-sensor2sample} shows that
the estimate obtained with our method (blue dots) did not
completely retrieved the magnetization distribution of the synthetic
sample (red dots), but is much better than that one obtained in the
previous test (blue dots in Figure \ref{fig:estimate-pre-processing}).
Notice that the observed data (Figures \ref{fig:datafit-sensor2sample}a, 
d, g and j) presents striations aligned with the acquisition lines
on each observation plane. This striations are produced by the
presence of position noise in the observation points.
Despite these striations, the (almost good) estimated magnetization 
distribution obtained by our method yields 
predicted data (Figures \ref{fig:datafit-sensor2sample}b, e, h and k) 
that recover the observed data (Figures \ref{fig:datafit-sensor2sample}a, 
d, g and j) in an acceptable manner.
This acceptable data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-sensor2sample}c, f, i and l).
The sample means $\mu$ are close to zero but the sample standard 
deviations $\sigma$ present some discrepancies with respect to
that one of the pseudo-random noise in magnetic data.
According to these histograms, the poorest data fit occurs in the 
observation plane $\alpha = 3$ (Figure \ref{fig:datafit-sensor2sample}l),
where the sample standard deviation $\sigma \approx 42$~$\mu$T.

These results illustrate the effects of errors in the sensor-to-sample
distance.
If compared with the results obtained in the previous test, 
the results obtained here suggest that our method is most robust against errors in
the sensor-to-sample distance than against misalignment errors.

@@

Figure \ref{fig:estimate-oda} shows that the estimate
obtained with our method (blue dots) completely retrieved the 
magnetization distribution of the simulated heterogeneous 
sample (red dots).
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-oda}b, e, h and k) that is very
close to the observed data (Figures \ref{fig:datafit-oda}a, 
d, g and j), except at the regions where the simulated spherical
grains are close to the sample surface.
The normalized histograms of the residuals between the predicted and
observed data (Figures \ref{fig:datafit-oda}c, f, i and l) show
sample means $\mu$ and sample standard deviations $\sigma$
very close to that ones of the pseudo-random noise 
contaminating the simulated magnetic data.

These results confirm the good performance of our method
in retrieving the magnetization distribution within a complex and
heterogeneous synthetic sample simulating a real ferro-manganese
crust.

@@

We inverted the observed magnetic data by using an
interpretation model which is formed by $P = 16$ prisms
and has side lengths equal to $L_{x} = 16$~mm, $L_{y} = 3$~mm 
and $L_{z} = 3$~mm along, respectively, the $x$, $y$ and 
$z$ axes.
Note that each prism forming the synthetic sample is 
approximated by four juxtaposed prisms of the 
interpretation model.
We considered a square magnetic sensor with active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}).
Figure \ref{fig:estimate-real} shows the estimated
magnetization distribution obtained with our method.
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-real}b, e, h and k) that recover
the main features in the observed data (Figures \ref{fig:datafit-real}a, 
d, g and j).
This coarse data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-real}c, f, i and l).
These histograms show non-null sample means $\mu$ and 
different sample standard deviations $\sigma$.

@@

We have presented a new method for inverting scanning magnetic
microscopy data with the purpose of estimating the internal 
magnetization distribution of a rectangular rock sample whose
internal magnetization distribution varies along one of its
axes.
Our method presents a new approach for automatically including
the averaging effect produced by the finite size of the 
magnetic sensor. Additionally, our method takes advantage 
of the geometry of a rectangular sample
to propose a new scanning design aiming at providing the magnetic
data not only on a single plane over the sample, but on four 
mutually orthogonal planes located around the sample.
The use of magnetic data located on the four planes instead
of a single one introduces independent information into the
linear system to be solved and consequently leads to a
a better conditioned inverse problem.

@@

These results show that our method could be an interesting complement
of traditional paleomagnetic techniques aiming at providing a 
non-destructive diagnostic of geological samples.
Nevertheless, further tests using either manufactured and geological samples 
need to be carried out with the purpose of validating our approach,
better evaluating the effects of position noise 
and misalignment problems during the scanning stage and
developing automatic pre-processing techniques.
By presuming that the internal magnetization of the rectangular 
sample varies along one of its axis we implicitly restrict the
application of our method to samples that are perpendicular
to the growth lamination within rocks.
It would be interesting to generalize our method in order to
remove this restriction and allow its application to estimate
complex magnetization distributions within rock samples.

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig6_LQ.png}
 \caption{Validation test. Comparison between the true (red dots)
 and estimated (blue and black dots) magnetization 
 (a) intensity, (b) inclination  and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black dashed lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on one the plane $\alpha = 0$,
 planes $\alpha = 0, 1$ and planes $\alpha = 0, 1, 2$
 are plotted, respectively, with high, intermediate and low 
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The black dashed lines in (b) and (c) indicate the $0^{\circ}$ value.}
 \label{fig:estimate-validation}
 \end{figure}

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig8_LQ.png}
 \caption{Pre-processing errors test. Comparison between the true (red dots)
 and estimated (blue and black dots) magnetization 
 (a) intensity, (b) inclination and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black dashed lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on one the plane $\alpha = 0$,
 planes $\alpha = 0, 1$ and planes $\alpha = 0, 1, 2$
 are plotted, respectively, with high, intermediate and low 
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The black dashed lines in (b) and (c) indicate the $0^{\circ}$ value.}
 \label{fig:estimate-pre-processing}
 \end{figure}

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig10_LQ.png}
 \caption{Sensor-to-sample distance test. Comparison between the true (red dots)
 and estimated (blue and black dots) magnetization 
 (a) intensity, (b) inclination and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black dashed lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on one the plane $\alpha = 0$, 
 planes $\alpha = 0, 1$ and planes 
 $\alpha = 0, 1, 2$ are plotted, respectively, with 
 high, intermediate and low transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The black dashed lines in (b) and (c) indicate the $0^{\circ}$ value.}
 \label{fig:estimate-sensor2sample}
 \end{figure}

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig15_LQ.png}
 \caption{Application to real data. Estimated magnetization 
 (a) intensity, (b) inclination and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black continuous lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on one the plane $\alpha = 0$,
 planes $\alpha = 0, 1$ and planes $\alpha = 0, 1, 2$ are
 plotted, respectively, with high, intermediate and low
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The continuous (vertical) black lines divide the estimated values 
 representing each prism forming the sample.
 The numbers indicate the index of each prism 
 (Figure \ref{fig:real-sample}c and Table \ref{tab:IRM-real-sample}.
 The black dashed (horizontal) lines in (b) indicate the values 
 $-90^{\circ}$, $0^{\circ}$, $45^{\circ}$ and $90^{\circ}$.
 The black dashed (horizontal) lines in (c) indicate the values 
 $0^{\circ}$ and $180^{\circ}$.
 The estimated values that are represented by black triangles are
 considered spurious due to the magnetite precipitation.}
 \label{fig:estimate-real}
 \end{figure}

>>>>

\usepackage{rotating}
\usepackage{amsmath}
\usepackage{url}

@@

Over the last decades, scanning magnetic microscopy techniques have 
been increasingly used in paleomagnetism and rock magnetism. 
Different from standard paleomagnetic magnetometers, scanning 
magnetic microscopes produce high-resolution maps of the vertical 
component of the magnetic induction field (flux density) 
on a plane located over the sample. 
These high-resolution magnetic maps can be used for estimating the 
magnetization distribution within a rock sample by inversion.
Previous studies have estimated the magnetization distribution 
within rock samples by inverting the magnetic data measured on a 
single plane above the sample. Here we present a new spatial domain
method for inverting the magnetic induction measured on four 
planes around the sample in order to retrieve its internal 
magnetization distribution. We have presumed that the internal 
magnetization distribution of the sample varies along one of
its axes. Our method approximates the sample geometry
by an interpretation model composed of a one-dimensional 
array of juxtaposed rectangular prisms with uniform magnetization. 
The Cartesian components of the magnetization vector 
within each rectangular prism 
are the parameters to be estimated by solving a linear inverse problem. 
Our method automatically deals with the averaging of 
the measured magnetic data due to the finite size of the magnetic sensor,
preventing the application of a deconvolution before the inversion.
Tests with synthetic data show the performance of our method in 
retrieving complex magnetization distributions even in 
the presence of magnetization heterogeneities. 
Moreover, they show the advantage of inverting the magnetic data on
four planes around the sample adn how this new acquisition scheme
improves the estimated magnetization distribution within the rock
sample.
We have also applied our method to invert experimentally measured 
magnetic data produced by a highly-magnetized synthetic sample 
that was manufactured in the laboratory.
The results show that, even in the presence of apparent position
noise, our method was able to retrieve the magnetization distribution
consistent with the isothermal remanent magnetization
induced in the sample.

@@

We have inverted magnetic data produced by
numerical simulations with the purpose of illustrating not only the 
good performance of our method in ideal cases, but also how
the estimated magnetization distribution obtained by our
method can be negatively impacted by the presence of position 
noise, errors in the sensor-to-sample distance and 
pre-processing errors in the observed data.
Our results also show the benefit of inverting a full data set
formed by magnetic data measured on four planes around the sample.
Tests with synthetic data simulating a real ferro-manganese
crust with magnetization heterogeneities show that our method 
can be used, for example, in fine-scale magnetostratigraphic 
studies.
We have also shown the results obtained by applying our method
to invert experimentally measured magnetic data produced by
a highly-magnetized synthetic sample that was manufactured in 
laboratory.
The results show that our method is able to estimate a magnetization
distribution that is consistent with the Isothermal Remanence 
Magnetization (IRM) induced in the
sample, even by inverting a magnetic data set that is contaminated 
by apparent position noise and were measured by a
custom-made magnetometer based on a Hall sensor.

@@

\subsection{Software implementation}
\label{subsec:Software implementation}

The inversion method proposed here is implemented in the Python programming
language.
Our implementation relies on the open-source library
numpy \citep[][ \url{http://scipy.org}]{jones2001, walt2011}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for geophysics specific tasks,
particularly for forward modeling using prisms.

The computational experiments
(e.g., data processing, synthetic tests, real data application)
were performed in
Jupyter (formerly IPython) notebooks
\citep[][ \url{http://jupyter.org/}]{perez2007}.
The notebook files combine the source code,
the results and figures generated by the code
and rich text to explain the analysis.

All source code, Jupyter notebooks, data, and results
can be found at the online repository
\url{https://github.com/pinga-lab/magnetization-rock-sample}.
An archived version of this repository is also available at
\url{http://dx.doi.org/...}
(\textbf{Note to reviewers: the archived version will be uploaded upon
publication}).

@@

Figure \ref{fig:estimate-validation} shows the four estimated 
magnetization distributions obtained by our method.
The one obtained by inverting the magnetic data on the 
four planes $\alpha = 0, 1, 2, 3$ is represented by the 
black dots and dashed lines. 
The three sets of blue dots and 
dashed lines represent the estimated magnetization distribution 
obtained by inverting the data located on the plane 
$\alpha = 0$, planes $\alpha = 0, 1$ and planes $\alpha = 0, 1, 2$,
which are plotted, respectively, with high, intermediate and low 
transparency.
All these estimates were obtained by using a regularization
parameter $\mu_{0} = 1 \times 10^{-10}$ (equation \ref{eq:goal-function}).
We can see that the estimated magnetization distribution 
obtained by inverting the full data set (black dots and black 
dashed lines in Figure \ref{fig:estimate-validation}) is the best one
in retrieving the true magnetization distribution
(red dots and red lines in Figure \ref{fig:estimate-validation}).
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-validation}b, e, h and k) that is very
close to the observed data (Figures \ref{fig:datafit-validation}a, 
d, g and j).
The normalized histograms of the residuals between the predicted and
observed data (Figures \ref{fig:datafit-validation}c, f, i and l) show
sample means $\mu$ and sample standard deviations $\sigma$
very close to that ones of the pseudo-random noise 
contaminating the simulated magnetic data.

@@

Figure \ref{fig:estimate-pre-processing} confirms the
the superiority of the estimated magnetization distribution 
obtained by inverting the full data set (black dots and 
black dashed lines) over the remaining three (blue dots and blue dashed lines).
All these estimates were obtained by using a regularization
parameter $\mu_{0} = 5 \times 10^{-2}$ (equation \ref{eq:goal-function}).
We can see, however, that even the estimate obtained with
the full data set failed in
retrieving the magnetization distribution of the simulated sample
(red dots). 
This poorly-estimated magnetization distribution yields 
predicted data (Figures \ref{fig:datafit-pre-processing}b, e, h and k) 
that do not
recover the observed data (Figures \ref{fig:datafit-pre-processing}a, 
d, g and j).
This coarse data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-pre-processing}c, f, i and l).
The sample means $\mu$ would be very close to the simulated 
constant bias and the sample standard deviations $\sigma$ would
be very close to that one of the pseudo-random noise 
if the magnetic data were properly corrected from
the misalignment problems.

These results exemplify the effects of not correcting the
misalignment problems prior to the inversion.
Besides, they show the advantage of inverting the full data set 
(data on the four planes).
As we can see, these problems lead to an estimated magnetization 
distribution that do not retrieves the true one and also
produce a coarse data fit.

@@

Unlike the previous tests, the distance $h$ 
(Figure \ref{fig:sample-planes-cross}) between the 
surface of the sample and the observation
points at each plane is not constant.
On each plane $\alpha = 0, 1, 2, 3$,
the observation points are located on a set 
of $42$ regularly-spaced acquisition 
lines, each one with $102$ regularly spaced points.
In this test, the distance $h$ is contaminated with a
Gaussian position noise having a common standard deviation of
$100$~$\mu$m and a different mean value equal to 
$420$~$\mu$m, $330$~$\mu$m, $400$~$\mu$m and $230$~$\mu$m
on each plane $\alpha = 0, 1, 2, 3$, respectively.
The distance $h$, however, is constant for observation points 
located on the same acquisition line.

@@

Figure \ref{fig:estimate-sensor2sample} shows the four
estimated magnetization distributions produced in this
test. All these estimates were obtained by using a regularization
parameter $\mu_{0} = 1 \times 10^{-10}$ (equation \ref{eq:goal-function}).
This figure also shows that,
as in the previous tests, the estimate obtained by 
inverting the full data set (black dots and black dashed lines) 
best approximates the true magnetization distribution
(red dots and red lines). However, even this estimate
did not completely retrieved the magnetization distribution of the synthetic
sample (red dots).
Notice that the observed data (Figures \ref{fig:datafit-sensor2sample}a, 
d, g and j) present striations aligned with the acquisition lines
on each observation plane. These striations are produced by the
presence of position noise in the observation points.
Despite these striations, the (almost good) estimated magnetization 
distribution obtained by inverting the full data set 
(black dots and black dashed lines in Figure \ref{fig:estimate-sensor2sample}) 
yields predicted data (Figures \ref{fig:datafit-sensor2sample}b, e, h and k) 
that recover the observed data (Figures \ref{fig:datafit-sensor2sample}a, 
d, g and j) in an acceptable manner.
This acceptable data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-sensor2sample}c, f, i and l).
The sample means $\mu$ are close to zero but the sample standard 
deviations $\sigma$ present some discrepancies with respect to
that one of the pseudo-random noise in magnetic data.
According to these histograms, the poorest data fit occurs in the 
observation plane $\alpha = 3$ (Figure \ref{fig:datafit-sensor2sample}l),
where the sample standard deviation $\sigma \approx 60$~$\mu$T.

These results illustrate the effects of errors in the sensor-to-sample
distance and also illustrate the advantage of inverting the full data set 
(data on the four planes).
If compared with the results obtained in the previous test, 
the results obtained here suggest that our method is most robust against errors in
the sensor-to-sample distance than against misalignment errors.

@@

Figure \ref{fig:estimate-oda} shows the four estimated 
magnetization distributions produced in this test.
All these estimates were obtained by using a regularization
parameter $\mu_{0} = 1 \times 10^{-10}$ (equation \ref{eq:goal-function}).
This figure also confirms that the estimate
obtained by inverting the full data set (black dots and black
dashed lines) is better than the remaining three (blue dots and blue
dashed lines) because it completely retrieved the 
magnetization distribution of the simulated heterogeneous 
sample (red dots).
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-oda}b, e, h and k) that is very
close to the observed data (Figures \ref{fig:datafit-oda}a, 
d, g and j), except at the regions where the simulated spherical
grains are close to the sample surface.
The normalized histograms of the residuals between the predicted and
observed data (Figures \ref{fig:datafit-oda}c, f, i and l) show
sample means $\mu$ and sample standard deviations $\sigma$
very close to that ones of the pseudo-random noise 
contaminating the simulated magnetic data.

As in all the previous tests, these results confirm the 
advantage of inverting the full data set (data on the four planes).
Moreover, they show the good performance of our method
in retrieving the magnetization distribution within a complex and
heterogeneous synthetic sample simulating a real ferro-manganese
crust.

@@

We inverted the observed magnetic data by using an
interpretation model which is formed by $P = 16$ prisms
and has side lengths equal to $L_{x} = 16$~mm, $L_{y} = 3$~mm 
and $L_{z} = 3$~mm along, respectively, the $x$, $y$ and 
$z$ axes.
Note that each prism forming the synthetic sample is 
approximated by four juxtaposed prisms of the 
interpretation model.
We considered a square magnetic sensor with active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}).
Figure \ref{fig:estimate-real} shows the four estimated
magnetization distribution obtained with our method.
All these estimates were obtained by using a regularization
parameter $\mu_{0} = 1 \times 10^{-10}$ (equation \ref{eq:goal-function}).
The black dots and black dashed lines represent the estimate
obtained by inverting the magnetic data on the four observation planes.
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-real}b, e, h and k) that recover
the main features in the observed data (Figures \ref{fig:datafit-real}a, 
d, g and j).
This coarse data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-real}c, f, i and l).
These histograms show non-null sample means $\mu$ and 
different sample standard deviations $\sigma$.

@@

We have presented a new method for inverting scanning magnetic
microscopy data with the purpose of estimating the internal 
magnetization distribution of a rectangular rock sample whose
internal magnetization distribution varies along one of its
axes.
Our method presents a new approach for automatically including
the averaging effect produced by the finite size of the 
magnetic sensor. Additionally, our method takes advantage 
of the geometry of a rectangular sample
to propose a new scanning design aiming at providing the magnetic
data not only on a single plane over the sample, but on four 
mutually orthogonal planes located around the sample.
The use of magnetic data located on the four planes instead
of a single one introduces independent information into the
linear system to be solved and consequently leads to a
a better conditioned inverse problem.
The advantage of inverting magnetic data located on four planes
around the sample is confirmed by all tests with synthetic data.

@@

These results show that our method could be an interesting complement
of traditional paleomagnetic techniques aiming at providing a 
non-destructive diagnostic of geological samples.
Nevertheless, further tests using either manufactured and geological samples 
need to be carried out with the purpose of validating our approach,
better evaluating the effects of position noise
and misalignment problems during the scanning stage and
also developing automatic pre-processing techniques.

By presuming that the internal magnetization of the rectangular 
sample varies along one of its axis we implicitly restrict the
application of our method to samples that are perpendicular
to the growth lamination within rocks.
It would be interesting to generalize our method in order to
remove this restriction and allow its application to estimate
complex magnetization distributions within rock samples.

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig6_LQ.png}
 \caption{Validation test. Comparison between the true (red dots)
 and estimated (blue and black dots) magnetization 
 (a) intensity, (b) inclination  and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black dashed lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on a single plane ($\alpha = 0$),
 two planes ($\alpha = 0, 1$) and three planes ($\alpha = 0, 1, 2$)
 are plotted, respectively, with high, intermediate and low 
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The black dashed lines in (b) and (c) indicate the $0^{\circ}$ value.}
 \label{fig:estimate-validation}
 \end{figure}

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig8_LQ.png}
 \caption{Pre-processing errors test. Comparison between the true (red dots)
 and estimated (blue and black dots) magnetization 
 (a) intensity, (b) inclination and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black dashed lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on a single plane ($\alpha = 0$),
 two planes ($\alpha = 0, 1$) and three planes ($\alpha = 0, 1, 2$)
 are plotted, respectively, with high, intermediate and low 
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The black dashed lines in (b) and (c) indicate the $0^{\circ}$ value.}
 \label{fig:estimate-pre-processing}
 \end{figure}

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig10_LQ.png}
 \caption{Sensor-to-sample distance test. Comparison between the true (red dots)
 and estimated (blue and black dots) magnetization 
 (a) intensity, (b) inclination and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black dashed lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on a single plane ($\alpha = 0$),
 two planes ($\alpha = 0, 1$) and three planes ($\alpha = 0, 1, 2$)
 are plotted, respectively, with high, intermediate and low 
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The black dashed lines in (b) and (c) indicate the $0^{\circ}$ value.}
 \label{fig:estimate-sensor2sample}
 \end{figure}

@@

 \begin{figure}
 \noindent \includegraphics[width=20pc]{Figs/Fig15_LQ.png}
 \caption{Application to real data. Estimated magnetization 
 (a) intensity, (b) inclination and (c) declination.
 The estimated magnetization distribution obtained by 
 inverting the magnetic data on the four planes $\alpha = 0, 1, 2, 3$
 is represented
 by the black dots and black continuous lines. The three sets of
 blue dots and dashed lines represent the estimated 
 magnetization distribution obtained by inverting the 
 magnetic data located on a single plane ($\alpha = 0$),
 two planes ($\alpha = 0, 1$) and three planes ($\alpha = 0, 1, 2$)
 are plotted, respectively, with high, intermediate and low 
 transparency.
 The values are plotted along the $x$-axis, at the center of each 
 prism forming the interpretation model.
 The continuous (vertical) black lines divide the estimated values 
 representing each prism forming the sample.
 The numbers indicate the index of each prism 
 (Figure \ref{fig:real-sample}c and Table \ref{tab:IRM-real-sample}.
 The black dashed (horizontal) lines in (b) indicate the values 
 $-90^{\circ}$, $0^{\circ}$, $45^{\circ}$ and $90^{\circ}$.
 The black dashed (horizontal) lines in (c) indicate the values 
 $0^{\circ}$ and $180^{\circ}$.
 The estimated values that are represented by black triangles are
 considered spurious due to the magnetite precipitation.}
 \label{fig:estimate-real}
 \end{figure}
